Visual Diagnostics of a Model Explainer -- Tools for the Assessment of LIME Explanations

### 2020-09-26 README.Rmd
trying to compare the data
updated to do list

- Edit dataset descriptions in README and add to the readme.txt document for submission
- Upload the files for submission and submit

@@

- `bullet-test.csv.zip` and `bullet-test.csv.zip` contain the data used for the bullet examples in the manuscript. Additional information about these files is included below under the heading "Additional Information on Bullet Data".
- `example-signatures.csv.zip` contains signature data from two matching bullet lands that is used to generate a figure in the manuscript.
- `raw` contains the raw versions of the data files (from Heike and CSAFE) that the above datasets are derived from. *Do not alter these files in any way.*

>>>>

- Move all code and results from our work identifying the data to my LIME-research-journals repo for future reference (including LIME explanations from different training datasets/models)
- Update 02-data-preparation.Rmd to only include the preparation of the CCFs_withlands data to be used in the paper
- Update code/figures in paper to train a random forest using CCFs_withlands data (and a set seed) and apply LIME predictions
- Rewrite Section 4 as needed
- Prepare for submission
- Edit dataset descriptions in README and add to the readme.txt document for submission
- Upload the files for submission and submit

@@

- `bullet-test.csv.zip` and `bullet-test.csv.zip` contain the data used for the bullet examples in the manuscript. Additional information about these files is included below under the heading "Additional Information on Bullet Data".
- `example-signatures.csv.zip` contains signature data from two matching bullet lands that is used to generate a figure in the manuscript.
- `raw` contains the raw versions of the data files (from Heike and CSAFE) that the above datasets are derived from. *Do not alter the data in these files.*
